---
title: "1A: Primary Analysis Models"
author: "Paul Bloom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(brms)
library(readr)
library(tidyr)

# Set seed for reproducible run
seed = 11291993

# for sufficient tail effective sample size
n_iter = 5000
```

# Prep data

* Put data in long format
* Recode internal details as `-0.5` and external details as `0.5`

```{r}
mem_data = readr::read_csv('../../data/autobio_interview_scores.csv') %>%
  dplyr::filter(is.na(exclude_trial), is.na(exclusion_reason))

session_data = readr::read_csv('../../data/session_data.csv') %>%
  dplyr::select(., participant_id, session, trial, familiarity)

mem_data = left_join(mem_data, session_data, by = c('participant_id', 'session', 'trial'))

mem_data_long = mem_data %>%
  tidyr::pivot_longer(c(total_external, total_internal), names_to = 'detail_type', values_to = 'num_details') %>%
  dplyr::mutate(detail_type = dplyr::recode(detail_type, 'total_internal'=-0.5, 'total_external'=0.5))
```

# Primary model for effects of condition on prompted recall (Primary analyses 1 & 3)


First set priors (very similar to brms/rstanarm defaults, although brms actually uses flat priors for population-level regression betas)

* population-level regresssion beta priors are t-distributions centered at 0, 3df, and a scale parameter of 10 
* standard deviations for participant-level effects are  similar t-distributions centered at 0, 3df, and a scale parameter of 10  (10 * the standard deviation of the outcome variable)
* `gamma(4,1)` prior for the degrees of freedom parameter for the t-distribution in the likelihood function (https://solomonkurz.netlify.app/post/2019-02-02-robust-linear-regression-with-student-s-t-distribution/)

```{r}
p = c(prior_string(paste0("student_t(3, 0, ", 10, ")"), class = "b"),
      prior_string(paste0("student_t(3, 0, ", 10*sd(mem_data_long$num_details), ")"), class = "sd"),
      prior_string("gamma(4, 1)", class = "nu"))
```


```{r}

m1_condition = brms::brm(data = mem_data_long, num_details ~ condition*detail_type + time*detail_type + 
                           (condition*detail_type + time*detail_type | participant_id), chains = 4, cores = 4,
                         family = 'student', prior = p,
                         seed = seed, iter = n_iter)

```

# Primary model for associations between familiarity & prompted recall (Primary analysis 2)

```{r}
m2_familiarity = data = mem_data_long %>%
  dplyr::filter(condition != 'control') %>%
  brms::brm(data = ., num_details ~ familiarity*detail_type + time*detail_type + 
              (familiarity*detail_type + time*detail_type | participant_id), chains = 4, cores = 4,
            family = 'student', prior = p, iter = n_iter, seed = seed)
```

# Save models for creating visualizatinos & extracting stats

```{r}
save(m1_condition, m2_familiarity, file = '../../results/models/primary_analysis_models.rda', compress = 'xz')
```