---
title: "Primary Planned Analysis Statistics"
author: "Paul Bloom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages

```{r, warning=FALSE, message=FALSE}
library(Matrix)
library(dbplyr)
library(tidyverse)
library(ggplot2)
library(brms)
library(cowplot)
library(tidybayes)
library(emmeans)
library(bayestestR)
library(DT)
theme_set(theme_bw())
```

### Load in data & models fit in `1a_primary_models.Rmd`

```{r load_data, message=FALSE}
mem_data = read_csv('../../data/autobio_interview_scores.csv')
load('../../results/models/primary_analysis_models.rda')
```

# Primary Analysis #1: Effects of familiar vs. unfamiliar music exposure on prompted memory recall (Fig. 5A-B)

* Since we modeled internal details & external details within the same model, we can use samples from the posterior predictive distribution to compute contrasts effects on *all details (sum of internal + external)* and *the percentage of details that were internal*.
* In general, all mathematical operations are computed separately for *each sample ('draw')* from the posterior predictive distributions, then summaries (medians + HDIs) are calculated at the end


### Draw posterior predictive distributions 

Make a "grid" of all combinations of condition, time, and detail_type to extract predictions for

```{r, warning=FALSE}
pred_grid = expand.grid(condition = c('U','F', 'C'), 
                        time = c('child', 'adol', 'adult'),
                        detail_type = c(-0.5, 0.5)) 

```

Using tidybayes, extract draws for the expected value (see [brms documentation](https://rdrr.io/cran/brms/man/posterior_epred.brmsfit.html)) of the posterior predictive distribution for each combination specified in `pred_grid`. The `re_formula=NA` argument specifies that uncertainty from random effects is not taken into account in extracting posterior predictions, so predictions are at the group (not individual participant) level.

```{r, warning=FALSE}
draws = m1_condition %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid, re_formula = NA) %>%
  dplyr::mutate(detail_type = dplyr::recode(detail_type, '-0.5'='total_internal', '0.5'='total_external'))
```

### From posterior predictive distributions, calculate average marginal means 

* Calculate  marginal means of posterior predictions for the average internal details, external details, proportion of internal details and total details (internal + internal)
* Marginal means are averaged across all time windows (child, adolescent, adult) but calculated *separately for each respective posterior sample (draw)* 


```{r, message=FALSE}
draws_wide = draws %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('condition', 'time', '.draw')) %>%
  mutate(internal_prop = total_internal / (total_internal + total_external),
         total = total_internal + total_external) %>%
  group_by(condition, .draw) %>%
  summarise(mean_internal = mean(total_internal), 
            mean_external = mean(total_external),
            mean_internal_prop = mean(internal_prop),
            mean_total = mean(total)) %>%
  mutate(condition = dplyr::recode(condition, 'U'='Unfamiliar Music', 'F'='Familiar Music', 'C'='Non-music Clips'))
```

### Create contrasts between familiar > unfamiliar music conditions through computing the average marginal effect (`diff`)

* Note: the estimates are multiplied by 100 for the proportion of internal details for ease of interpretation/visualization -- now they are the estimated effects on the *percentage* of internal details
* 4 measures here for `Internal Details`, `External Details`, `All Details (Internal + External)`, and `% of Details Internal`

```{r}
draws_wide_comparison_familiar_unfamiliar = draws_wide %>%
  pivot_longer(contains('mean')) %>%
  pivot_wider(names_from = condition, values_from = value, id_cols = c(.draw, name)) %>%
  dplyr::mutate(diff = `Familiar Music`-`Unfamiliar Music`,
                diff = ifelse(name == 'mean_internal_prop', 100*diff, diff),
                name = dplyr::recode(name,
                                     'mean_total'='All Details\n(Internal + External)',
                                     'mean_internal_prop' = '% of Details Internal',
                                     'mean_internal' = 'Internal Details',
                                     'mean_external' = 'External Details'))
```

### Summarise the posterior median and 95% HDI for the average marginal effect of familiar > unfamiliar music on each outcome (Primary Analysis #1)

```{r}
draws_wide_comparison_familiar_unfamiliar %>%
  group_by(name) %>%
  summarise(mean = mean(diff), interval = bayestestR::hdi(diff)) %>%
  unnest(interval) %>%
  DT::datatable()
```


# Primary Analysis #2: Associations between ratings of song familiarity and prompted memory recall (Fig. 6)


### Use `emmeans::emtrends()` to get marginal associations of familiarity with # of internal details and external details recalled

`gather_emmeans_draws()` creates a dataframe with all posterior samples for the marginal associations calculated by `emtrends()`

```{r}
familiarity_trends = m2_familiarity %>% 
  emmeans::emtrends(~detail_type, var = 'familiarity', epred = TRUE) %>%
  gather_emmeans_draws() %>%
  dplyr::mutate(detail_type = dplyr::recode(detail_type, '-0.5'='total_internal', '0.5'='total_external'))
```

Wrangle emtrends data

```{r}
familiarity_trends = familiarity_trends %>%
  pivot_wider(id_cols = .draw, names_from = detail_type, values_from = .value) %>%
  mutate(all_detail = total_external + total_internal) %>%
  pivot_longer(-.draw) %>%
  dplyr::mutate(name = dplyr::recode(name,  'all_detail'='All Details\n(Internal + External)',
                                     'total_internal' = 'Internal Details',
                                     'total_external' = 'External Details'))
```

### Make a grid including all possible values of familiarity (1:5) to make posterior predictions

```{r}
pred_grid_familiarity = expand.grid(familiarity = 1:5,
                        time = c('child', 'adol', 'adult'),
                        detail_type = c(-0.5, 0.5)) 

```

As before, use `tidybayes::add_fitted_draws()` to extract the expected value of the posterior predictive distribution for each combination specified in `pred_grid_familiarity`, not including uncertainty from random effects. 

```{r, warning=FALSE}
draws_familiarity = m2_familiarity %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_familiarity, re_formula = NA) %>%
  dplyr::mutate(detail_type = dplyr::recode(detail_type, "-0.5"='total_internal', "0.5"='total_external')) %>%
  group_by(familiarity, detail_type, .draw) %>%
  summarise(mean_details = mean(.value)) 
```

### Calculate associations betwen familiarity and the percentage of details internal

This step is a little more involved, since `emtrends()` will not directly compute the marginal slopes for this transformed outcome. Here, the steps are:

* For each posterior draw, calculate `internal_proportion` (the estimated proportion of details that are internal) for each possible value of `familiarity`
* Group the data by draw, then for each draw run a linear regression to calculate the *slope* of internal proportion with regards to familiarity (basically what `emtrends()` is doing under the hood)
* Multiply these slopes from linear regression models by 100 to get the posterior distribution for the estimated relationship between familiarity and the *percentage* of details internal (easier to visualize on the same scale as other posterior distributions)

```{r}
familarity_draws_wide = draws_familiarity %>%
  pivot_wider(names_from = detail_type, values_from = mean_details, id_cols = c('.draw', 'familiarity')) %>%
  mutate(internal_proportion = total_internal / (total_internal + total_external)) %>%
  group_by(.draw) %>%
  nest() %>%
  mutate(slope = purrr::map(data, ~lm(data = ., internal_proportion ~ familiarity)$coefficients[2]*100)) %>%
  unnest(slope) %>%
  dplyr::select(-data, .draw, value=slope) %>%
  dplyr::mutate(name = '% of Details Internal') 
```

### Put posterior calculations together and calculate HDIs for all associations 
```{r}
familiarity_trends = rbind(familiarity_trends, familarity_draws_wide)

familiarity_trends %>%
  group_by(name) %>%
  summarise(mean = mean(value), interval = bayestestR::hdi(value)) %>%
  unnest(interval) %>%
  DT::datatable()
```

# Primary Analysis #3: Effects of music vs. non-music clips on prompted memory recall (Fig. 5A & C)

First, group posterior predictions from both the familiar music & unfamiliar music conditions together and average them. 

```{r}
draws_music_no_music = mutate(draws, condition = ifelse(condition == 'C', 'No Music', 'Music')) %>%
  group_by(condition, time, detail_type, .draw) %>%
  summarise(.value = mean(.value)) %>%
  ungroup()
```

### From posterior predictive distributions, calculate average marginal means 

Average marginal means are created in the same way previously described for Primary Analysis #1

```{r}
draws_wide_music_no_music = draws_music_no_music %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('condition', 'time', '.draw')) %>%
  mutate(internal_prop = total_internal / (total_internal + total_external),
         total = total_internal + total_external) %>%
  group_by(condition, .draw) %>%
  summarise(mean_internal = mean(total_internal), 
            mean_external = mean(total_external),
            mean_internal_prop = mean(internal_prop),
            mean_total = mean(total))

```

### Create contrasts between all music > no music conditions through computing the average marginal effect (`diff`)

Same contrasts as above for Familiar Music > Unfamiliar music


```{r}
draws_wide_comparison_music_no_music = draws_wide_music_no_music %>%
  pivot_longer(contains('mean')) %>%
  pivot_wider(names_from = condition, values_from = value, id_cols = c(.draw, name)) %>%
  dplyr::mutate(diff = `Music`-`No Music`,
                diff = ifelse(name == 'mean_internal_prop', 100*diff, diff),
                name = dplyr::recode(name,
                                     'mean_total'='All Details\n(Internal + External)',
                                     'mean_internal_prop' = '% of Details Internal',
                                     'mean_internal' = 'Internal Details',
                                     'mean_external' = 'External Details'))
```

### Summarise the posterior median and 95% HDI for the average marginal effect of familiar > unfamiliar music on each outcome (Primary Analysis #3)

```{r}
draws_wide_comparison_music_no_music %>%
  group_by(name) %>%
  summarise(mean = mean(diff), interval = bayestestR::hdi(diff)) %>%
  unnest(interval) %>%
  DT::datatable()
```
