---
title: "2C: Secondary Analysis Stats"
author: "Paul Bloom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(ggplot2)
library(brms)
library(cowplot)
library(tidybayes)
library(emmeans)
library(DT)
```

### Load data & models

```{r, warning=FALSE, message=FALSE}
load('../../results/models/secondary_models.rda')
session_data = read_csv('../../data/session_data.csv')
mem_data = read_csv('../../data/autobio_interview_scores.csv') %>%
  dplyr::filter(is.na(exclude_trial)) 
```


# Effects of music manipulation on clip-evoked affect (sFig. 9A)

Differences in participant-reported affect evoked by clips in each condition. The table below shows posterior medians and 95% HDI, on the probit scale.  

```{r, warning=FALSE, message=FALSE}
emmeans::emmeans(m1_mood, specs = 'condition') %>%
  pairs() %>%
  as.data.frame() %>%
  DT::datatable()
```


# Associations between clip-evoked affect and prompted memory recall (sFig. 9B-C)

Similar to primary analysis 2 with familiarity (see `1a_primary_analysis/1c_primary_stats.Rmd`), use emmeans::emtrends() and separate linear regressions to calculate marginal associations between affect and prompted memory recall of internal & external details. 

```{r}
mood_deliberate_trends = m2_mood_recall %>% 
  emmeans::emtrends(~detail_type, var = 'music_evoked_affect', epred = TRUE) %>%
  gather_emmeans_draws()

mood_deliberate_trends = mood_deliberate_trends %>%
  pivot_wider(id_cols = .draw, names_from = detail_type, values_from = .value) %>%
  mutate(all_detail = (total_external + total_internal)/2) %>%
  pivot_longer(-.draw) %>%
  dplyr::mutate(name = dplyr::recode(name,  'all_detail'='All Details\n(Internal + External)',
                                     'total_internal' = 'Internal Details',
                                     'total_external' = 'External Details'))
```

## Get draws, manually calculate slopes for % of details that are internal

Set up a grid of all possible values of music-evoked affect (1-7) to make posterior predictions for. As before, use `tidybayes::add_fitted_draws()` to extract the expected value of the posterior predictive distribution for each combination specified in `pred_grid_mood_recall`, not including uncertainty from random effects. 


```{r, warning=FALSE}
pred_grid_mood_recall = expand.grid(music_evoked_affect = 1:7,
                        time = c('child', 'adol', 'adult'),
                        detail_type = c('total_internal', 'total_external'))

draws_mood_recall = m2_mood_recall %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_mood_recall, re_formula = NA) %>%
  group_by(music_evoked_affect, detail_type, .draw) %>%
  summarise(mean_details = mean(.value)) 
```

As with primary analyses, this step is a little more involved, since `emtrends()` will not directly compute the marginal slopes for this transformed outcome. Here, the steps are:

* For each posterior draw, calculate `internal_proportion` (the estimated proportion of details that are internal) for each possible value of `music_evoked_affect`
* Group the data by draw, then for each draw run a linear regression to calculate the *slope* of internal proportion with regards to `music_evoked_affect` (basically what `emtrends()` is doing under the hood)
* Multiply these slopes from linear regression models by 100 to get the posterior distribution for the estimated relationship between music-evoked affect and the *percentage* of details internal (easier to visualize on the same scale as other posterior distributions)

```{r}
draws_mood_recall_wide = draws_mood_recall %>%
  pivot_wider(names_from = detail_type, values_from = mean_details, id_cols = c('.draw', 'music_evoked_affect')) %>%
  mutate(internal_proportion = total_internal / (total_internal + total_external)) %>%
  group_by(.draw) %>%
  nest() %>%
  mutate(slope = purrr::map(data, ~lm(data = ., internal_proportion ~ music_evoked_affect)$coefficients[2]*100)) %>%
  unnest(slope) %>%
  dplyr::select(-data, .draw, value=slope) %>%
  dplyr::mutate(name = '% of Details Internal')

```

Put posterior calculations together and calculate HDIs for all associations between music-evoked affect and prompted recall

```{r}
mood_deliberate_trends = rbind(mood_deliberate_trends, draws_mood_recall_wide)

mood_deliberate_trends %>%
  group_by(name) %>%
  summarise(mean = mean(value),
            interval = bayestestR::hdi(value)) %>%
  unnest(interval) %>%
  DT::datatable()
```


# Associations between spontaneous and prompted memory recall (sFig. 11)

First, extract posterior predictions as before, then compute all contrasts for each posterior draw. 

```{r, warning=FALSE, message=FALSE}
pred_grid_spontaneous = expand.grid(spont_memory = c('y', 'n'),
                        detail_type = c('total_internal', 'total_external'))

draws_spontaneous = m3_spontaneous_recall %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_spontaneous, re_formula = NA) 

draws_spontaneous_wide = draws_spontaneous %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('spont_memory', '.draw')) %>%
  mutate(internal_prop = total_internal / (total_internal + total_external),
         total = total_internal + total_external) %>%
  group_by(spont_memory, .draw) %>%
  summarise(mean_internal = mean(total_internal), 
            mean_external = mean(total_external),
            mean_internal_prop = mean(internal_prop),
            mean_total = mean(total)) 

draws_wide_comparison_spontaneous= draws_spontaneous_wide %>%
  pivot_longer(contains('mean')) %>%
  pivot_wider(names_from = spont_memory, values_from = value, id_cols = c(.draw, name)) %>%
  dplyr::mutate(diff = `y`-`n`,
                diff = ifelse(name == 'mean_internal_prop', 100*diff, diff),
                name = dplyr::recode(name,
                                     'mean_total'='All Details\n(Internal + External)',
                                     'mean_internal_prop' = '% of Details Internal',
                                     'mean_internal' = 'Internal Details',
                                     'mean_external' = 'External Details'))

```

Summarise posterior contrasts with medians + 95% HDIs. 

```{r}
draws_wide_comparison_spontaneous %>%
  group_by(name) %>%
  summarise(mean = mean(diff),
            interval = bayestestR::hdi(diff)) %>%
  unnest(interval) %>%
  DT::datatable()
```


# Associations between music exposure during the time period of release and prompted recall

Here, 2 versions of the analysis are reported:

* The preregistered version, which does not contain covariates for time (and arguably is then confounded by the time period of the prompted memory)
* An alternate model that does covary for time (not preregistered)

## Preregistered version (no covariates)


```{r, warning=FALSE, message=FALSE}
pred_grid_matching_recall = expand.grid(music_exposure_matching = 1:5,
                                        music_exposure_nonmatching = 1:5,
                        detail_type = c('total_internal', 'total_external'))

timed_exposure_trends_matching = m4_timed_exposure_recall %>% emmeans::emtrends(~detail_type, var = 'music_exposure_matching', epred = TRUE) %>%
  gather_emmeans_draws() %>%
  mutate(type = 'matching') %>%
  pivot_wider(id_cols = .draw, names_from = detail_type, values_from = .value) %>%
  mutate(all_detail = (total_external + total_internal)/2) %>%
  pivot_longer(-.draw) %>%
  dplyr::mutate(name = dplyr::recode(name,  'all_detail'='All Details\n(Internal + External)',
                                     'total_internal' = 'Internal Details',
                                     'total_external' = 'External Details'))


draws_matching = m4_timed_exposure_recall %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_matching_recall, re_formula = NA) %>%
  group_by(music_exposure_matching, detail_type, .draw) %>%
  summarise(.value = mean(.value)) 

draws_matching_wide = draws_matching %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('.draw', 'music_exposure_matching')) %>%
  mutate(internal_proportion = total_internal / (total_internal + total_external)) %>%
  group_by(.draw) %>%
  nest() %>%
  mutate(slope = purrr::map(data, 
                            ~lm(data = ., internal_proportion ~ music_exposure_matching)$coefficients[2]*100)) %>%
  unnest(slope) %>%
  dplyr::select(-data, .draw, value=slope) %>%
  dplyr::mutate(name = '% of Details Internal') 

timed_exposure_trends_matching = rbind(timed_exposure_trends_matching, draws_matching_wide) %>%
  mutate(match = 'Time window of song release')

timed_exposure_trends_nonmatching = m4_timed_exposure_recall %>% emmeans::emtrends(~detail_type, var = 'music_exposure_nonmatching', epred = TRUE) %>%
  gather_emmeans_draws() %>%
  mutate(type = 'matching') %>%
  pivot_wider(id_cols = .draw, names_from = detail_type, values_from = .value) %>%
  mutate(all_detail = (total_external + total_internal)/2) %>%
  pivot_longer(-.draw) %>%
  dplyr::mutate(name = dplyr::recode(name,  'all_detail'='All Details\n(Internal + External)',
                                     'total_internal' = 'Internal Details',
                                     'total_external' = 'External Details'))

draws_nonmatching = m4_timed_exposure_recall %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_matching_recall, re_formula = NA) %>%
  group_by(music_exposure_nonmatching, detail_type, .draw) %>%
  summarise(.value = mean(.value)) 

draws_nonmatching_wide = draws_nonmatching %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('.draw', 'music_exposure_nonmatching')) %>%
  mutate(internal_proportion = total_internal / (total_internal + total_external)) %>%
  group_by(.draw) %>%
  nest() %>%
  mutate(slope = purrr::map(data, ~lm(data = ., internal_proportion ~ music_exposure_nonmatching)$coefficients[2]*100)) %>%
  unnest(slope) %>%
  dplyr::select(-data, .draw, value=slope) %>%
  dplyr::mutate(name = '% of Details Internal') 

timed_exposure_trends_nonmatching = rbind(timed_exposure_trends_nonmatching, draws_nonmatching_wide) %>%
  mutate(match = 'All other time windows')

timed_exposure = rbind(timed_exposure_trends_matching, timed_exposure_trends_nonmatching)
timed_exposure$match = factor(timed_exposure$match, levels = c('Time window of song release','All other time windows'))

```

# Timed Exposure Modified Analysis (covarying for time)

```{r}
pred_grid_alt_matching_recall = expand.grid(music_exposure_matching = 1:5,
                                        music_exposure_nonmatching = 1:5,
                                        time = c('child', 'adol', 'adult'),
                        detail_type = c('total_internal', 'total_external'))

timed_exposure_trends_alt_matching = m5_alt_timed_exposure_recall %>% emmeans::emtrends(~detail_type, var = 'music_exposure_matching', epred = TRUE) %>%
  gather_emmeans_draws() %>%
  mutate(type = 'alt_matching') %>%
  pivot_wider(id_cols = .draw, names_from = detail_type, values_from = .value) %>%
  mutate(all_detail = (total_external + total_internal)/2) %>%
  pivot_longer(-.draw) %>%
  dplyr::mutate(name = dplyr::recode(name,  'all_detail'='All Details\n(Internal + External)',
                                     'total_internal' = 'Internal Details',
                                     'total_external' = 'External Details'))

draws_alt_matching = m5_alt_timed_exposure_recall %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_alt_matching_recall, re_formula = NA) %>%
  group_by(music_exposure_matching, detail_type, .draw) %>%
  summarise(.value = mean(.value)) 

draws_alt_matching_wide = draws_alt_matching %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('.draw', 'music_exposure_matching')) %>%
  mutate(internal_proportion = total_internal / (total_internal + total_external)) %>%
  group_by(.draw) %>%
  nest() %>%
  mutate(slope = purrr::map(data, ~lm(data = ., internal_proportion ~ music_exposure_matching)$coefficients[2]*100)) %>%
  unnest(slope) %>%
  dplyr::select(-data, .draw, value=slope) %>%
  dplyr::mutate(name = '% of Details Internal') 

timed_exposure_trends_alt_matching = rbind(timed_exposure_trends_alt_matching, draws_alt_matching_wide) %>%
  mutate(match = 'Time window of song release')


timed_exposure_trends_alt_nonmatching = m5_alt_timed_exposure_recall %>% emmeans::emtrends(~detail_type, var = 'music_exposure_nonmatching', epred = TRUE) %>%
  gather_emmeans_draws() %>%
  mutate(type = 'alt_matching') %>%
  pivot_wider(id_cols = .draw, names_from = detail_type, values_from = .value) %>%
  mutate(all_detail = (total_external + total_internal)/2) %>%
  pivot_longer(-.draw) %>%
  dplyr::mutate(name = dplyr::recode(name,  'all_detail'='All Details\n(Internal + External)',
                                     'total_internal' = 'Internal Details',
                                     'total_external' = 'External Details'))

draws_alt_nonmatching = m5_alt_timed_exposure_recall %>% 
  tidybayes::add_fitted_draws(newdata = pred_grid_alt_matching_recall, re_formula = NA) %>%
  group_by(music_exposure_nonmatching, detail_type, .draw) %>%
  summarise(.value = mean(.value)) 

draws_alt_nonmatching_wide = draws_alt_nonmatching %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('.draw', 'music_exposure_nonmatching')) %>%
  mutate(internal_proportion = total_internal / (total_internal + total_external)) %>%
  group_by(.draw) %>%
  nest() %>%
  mutate(slope = purrr::map(data, ~lm(data = ., internal_proportion ~ music_exposure_nonmatching)$coefficients[2]*100)) %>%
  unnest(slope) %>%
  dplyr::select(-data, .draw, value=slope) %>%
  dplyr::mutate(name = '% of Details Internal') 

timed_exposure_trends_alt_nonmatching = rbind(timed_exposure_trends_alt_nonmatching, draws_alt_nonmatching_wide) %>%
  mutate(match = 'All other time windows')


timed_exposure_alt = rbind(timed_exposure_trends_alt_matching, timed_exposure_trends_alt_nonmatching)
timed_exposure_alt$match = factor(timed_exposure_alt$match, levels = c('Time window of song release','All other time windows'))

```

# Timed Exposure: contrast betas & HDIs

## No time period covariates

```{r}
timed_exposure %>%
  group_by(name, match) %>%
  summarise(mean = mean(value),
            hdi = bayestestR::hdi(value, ci = 0.95)) %>%
  unnest(hdi) %>%
  DT::datatable()
```

## Covarying for time period

```{r}
timed_exposure_alt %>%
  group_by(name, match) %>%
  summarise(mean = mean(value),
    hdi = bayestestR::hdi(value)) %>%
  unnest(hdi) %>%
  DT::datatable()
```

# HDIs corrected for multiple comparisons

Not covarying for time period

```{r}
corrected_interval_calcs = timed_exposure %>%
  dplyr::filter(name %in% c('External Details', 'Internal Details')) %>%
  group_by(name, match) %>%
  summarise(proportion_consistent = case_when(
    median(value) >= 0 ~ sum(value >= 0)/n(),
    median(value) < 0 ~ sum(value < 0)/n())) %>%
  ungroup() %>%
  mutate(rank = rank(proportion_consistent),
         width = 1 - (0.05/rank),
         upr_corrected = 1 - (0.05/2)/rank,
         lwr_corrected = 1 - upr_corrected)


corrected_intervals = timed_exposure %>%
  dplyr::filter(name %in% c('External Details', 'Internal Details')) %>%
  left_join(corrected_interval_calcs, by = c('name', 'match')) %>%
  group_by(name, match) %>%
  summarise(mean = mean(value),
            rank = rank[1],
            hdi = bayestestR::hdi(value, ci = width[1])) %>%
  unnest(hdi)

corrected_intervals %>%
  DT::datatable()
```

