---
title: "Exploratory Analysis: Differences in prompted recall as a function of age at the time of the prompted event (Fig. 9)"
author: "Paul Bloom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Matrix)
library(dbplyr)
library(tidyverse)
library(ggplot2)
library(brms)
library(cowplot)
library(tidybayes)
library(emmeans)
library(bayestestR)
library(DT)
theme_set(theme_bw())
```

### Load data and model from primary analysis

```{r, warning=FALSE, message=FALSE}
mem_data = read_csv('../../data/autobio_interview_scores.csv')
load('../../results/models/primary_analysis_models.rda')
```
## Draw posterior predictive distributions 

As with primary analysis, make a "grid" of all combinations of condition, time, and detail_type to extract predictions for

```{r, warning=FALSE}
pred_grid = expand.grid(condition = c('U','F', 'C'), 
                        time = c('child', 'adol', 'adult'),
                        detail_type = c(-0.5, 0.5)) 

draws = m1_condition %>% tidybayes::add_fitted_draws(newdata = pred_grid, re_formula = NA) %>%
  dplyr::mutate(detail_type = dplyr::recode(detail_type, '-0.5'='total_internal', '0.5'='total_external'))
```

## Summarise posterior predictions grouped by the time period and detail tyle (internal vs. external)

Still keep each draw separate here, so that the total number of details and proportion of internal details can be calculated for each posterior sample. 

```{r, warning=FALSE, message=FALSE}
draws_dev = draws %>%
  group_by(time, detail_type, .draw) %>%
  summarise(.value = mean(.value)) %>%
  ungroup()

draws_dev_wide = draws_dev %>%
  pivot_wider(names_from = detail_type, values_from = .value, id_cols = c('time', '.draw')) %>%
  mutate(internal_prop = total_internal / (total_internal + total_external),
         total = total_internal + total_external) %>%
  group_by(time, .draw) %>%
  summarise(mean_internal = mean(total_internal), 
            mean_external = mean(total_external),
            mean_internal_prop = mean(internal_prop),
            mean_total = mean(total))
```
## Set up all pairwise comparisons between time periods (childhood, adolescence, young adulthood)

As in primary analyses, multiply proportion of internal details by 100 to become the percentage of internal details (for visualization & reporting)

```{r}
draws_dev_wide_comparison = draws_dev_wide %>%
  pivot_longer(contains('mean')) %>%
  pivot_wider(names_from = time, values_from = value, id_cols = c(.draw, name)) %>%
  dplyr::mutate(diff_adol = `adol`-`child`,
                diff_adult = `adult`-`adol`,
                diff_adult_child = `adult` - `child`,
                diff_adol = ifelse(name == 'mean_internal_prop', 100*diff_adol, diff_adol),
                diff_adult = ifelse(name == 'mean_internal_prop', 100*diff_adult, diff_adult),
                diff_adult_child = ifelse(name == 'mean_internal_prop', 100*diff_adult_child, diff_adult_child),
                name = dplyr::recode(name,
                                     'mean_total'='All Details\n(Internal + External)',
                                     'mean_internal_prop' = '% of Details Internal',
                                     'mean_internal' = 'Internal Details',
                                     'mean_external' = 'External Details')) %>%
  pivot_longer(contains('diff'), names_to = 'contrast_name', values_to = 'value') %>%
  dplyr::mutate(contrast_name = dplyr::recode(contrast_name,
                                              'diff_adol' = ' Adolescence > Childhood', 
                                              'diff_adult_child' =  ' Young Adulthood > Childhood',
                                              'diff_adult' = 'Young Adulthood > Adolescence'))
```

## Plot posterior distributions for each contrast for each outcome measure

```{r}
dev_comparisons_plot = ggplot(draws_dev_wide_comparison, aes(x = value, y = name)) +
  geom_vline(xintercept = 0, lty = 2) +
  stat_halfeye(.width = 0.95) +
  theme_bw() +
  labs(x = '', y = '\n', title = 'Contrast Posterior Distributions') +
  facet_grid(~contrast_name) +
  theme(text = element_text(face = 'bold'), 
        axis.text = element_text(size = 11), axis.title = element_text(size = 14),
        strip.text = element_text(size = 12))
```

## Plot the posterior predictions themselves

```{r}
dev_plot = draws_dev_wide %>%
  pivot_longer(c(mean_internal, mean_external)) %>%
  mutate(name = dplyr::recode(name, 'mean_external'='External Details', 'mean_internal'=' Internal Details'),
         time = dplyr::recode(time, 'child'='Childhood\n5-9 years old', 'adol' = 'Adolescence\n14-18 years old',
                              'adult' = 'Young Adulthood\n20-25 years old')) %>%
  ggplot(data = ., aes(x = time, y = value, fill = time)) +
  facet_wrap(~name) +
  stat_halfeye(.width = 0.95) +
  theme(legend.position = 'none') +
  labs(x = 'Time Period of Event', y = '# of Details') +
  scale_fill_brewer(type = 'qual') +
  theme(text = element_text(face = 'bold'), 
        axis.text = element_text(size = 11), axis.title = element_text(size = 14),
        strip.text = element_text(size = 12))
```

Put plots together in grid for Fig. 9

```{r}
dev_grid = cowplot::plot_grid(dev_plot, dev_comparisons_plot, nrow = 2, labels = c('A', 'B'), rel_heights = c(1.5, 1), align = 'v', axis = 'lr')
cowplot::save_plot(dev_grid, filename = '../../results/fig9_developmental_grid.png', base_height = 8, base_width = 12.7)
```

# Stats for Differences in prompted recall as a function of age at the time of the prompted event (Fig. 9)

Posterior medians and 95% HDIs. 

```{r, message=FALSE, warning=FALSE}
draws_dev_wide_comparison %>%
  group_by(name, contrast_name) %>%
  summarise(mean = mean(value),
            d = bayestestR::hdi(value)) %>%
  unnest(d) %>%
  DT::datatable()
```