---
title: "Get Pilot Data Metrics"
author: "Paul A. Bloom"
date: "October 23, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(corrplot)
library(brms)
```

# Read in pilot data

This is the raw but deidentified sentence-level pilot data scored for details in each sentence 

```{r}
# one row per sentence
pilotData = read.csv('data/cleanPilotData.csv', stringsAsFactors = FALSE)
```

# Derive parameters for understanding pilots and sample size calculations
```{r}
# condense to one row per memory, calculate internal details, external details, and sentences per memory
pilotMem = pilotData %>%
  group_by(subjectID, session, memoryNumber, timePeriod, condition, memory) %>%
  summarize(internal = sum(totalInternal),
            external = sum(totalExternal),
            sentences = max(sentenceNum),
            duration = duration[1])

# get the standard deviation across memories for each subject!
pilotMemSd = pilotMem %>%
  ungroup() %>%
  group_by(subjectID) %>%
  summarize(internalSD = sd(internal),
            externalSD = sd(external),
            internalMean = mean(internal),
            externalMean = mean(external),
            n = n()) %>%
  dplyr::filter(., !(internalSD == 0 & internalMean == 0)) %>% # filter out memories with no details
  dplyr::select(-internalMean, -externalMean)
```

# In this chunk, run some quick regressions (separately for each subject) to get rough estimates of subject-level 'effects' of developmental time period

These also give us intercepts
```{r}
# effects of time period on internal details
timePeriodEffectsInternal = pilotMem %>%
  group_by(subjectID) %>%
  nest() %>%
  mutate(., reg = map(data, ~lm(data = ., internal ~ timePeriod)), 
         coefs = map(reg, ~broom::tidy(.))) %>%
  unnest(coefs) %>%
  dplyr::select(., subjectID, term, estimate) %>%
  tidyr::spread(., key = term, value = estimate) %>%
  dplyr::select(subjectID, internal_intercept = `(Intercept)`, internal_time_c = timePeriodC, internal_time_t = timePeriodT)


# effects of time period on external details
timePeriodEffectsExternal = pilotMem %>%
  group_by(subjectID) %>%
  nest() %>%
  mutate(., reg = map(data, ~lm(data = ., external ~ timePeriod)), 
         coefs = map(reg, ~broom::tidy(.))) %>%
  unnest(coefs) %>%
  dplyr::select(., subjectID, term, estimate) %>%
  tidyr::spread(., key = term, value = estimate) %>%
  dplyr::select(subjectID, external_intercept = `(Intercept)`, external_time_c = timePeriodC, external_time_t = timePeriodT)


```

# Here, generate correlations for each participant between external and internal details
```{r}
internalExternalCor = pilotMem %>%
  group_by(subjectID) %>%
  nest() %>%
  mutate(., cor_internal_external = map(data, ~cor(.$internal, .$external, method = 'pearson'))) %>%
  unnest(cor_internal_external) %>%
  dplyr::select(-data)
```

# Save all out for use in simulations
```{r}
sim_params = left_join(timePeriodEffectsExternal, timePeriodEffectsInternal, by = 'subjectID') %>%
  left_join(., internalExternalCor, by = 'subjectID') %>%
  left_join(., pilotMemSd, by = 'subjectID')

write.csv(sim_params, row.names = FALSE, file = 'data/power_sim_params.csv')
```

