---
title: "sample_size_graphs"
author: "Paul Bloom"
date: "8/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Pull in simulation csv files and merge to a master file

```{r}
for (folder in dir('data/sim_models/')){
  for (iter in 1:100){
    tmp = read_csv(paste0('data/sim_models/', folder, '/model_summary_', iter, '.csv'))
    tmp$effect_size = folder
    if (iter == 1 & folder == 'effect_1_detail_100_subs'){
      comb = tmp
    }else{
      comb = rbind(comb, tmp)
    }
  }
}

# write master file to csv
write.csv(comb, file = 'data/simulated_study_model_params.csv', row.names = FALSE)
```


# Clean simulation data a little bit for the key interaction parameter

Here, we're just looking for the interaction between the effect of the familiar music condition and internal vs. external details
This should be the hardest of the key effects to estimate


Recovering a parameter is defined as the approx 95% CI not overlapping 0, and the true effect size being contained in the 95% CI
```{r}
# power for the interaction between familiarity & detail type
interact_sims = comb %>% 
  dplyr::filter(term == 'condunfamiliar:type') %>%
  mutate(sample_size = ifelse(grepl('100', effect_size), 100, 75),
        effect_size = case_when(
            grepl('effect_1_', effect_size) ~ 1,
            grepl('effect_1.5_', effect_size) ~ 1.5,
            grepl('effect_2_', effect_size) ~ 2,
            grepl('effect_2.5_', effect_size) ~ 2.5,
            grepl('effect_3_', effect_size) ~ 3,
         ),
         lwr = estimate -2.0*std.error,
         upr = estimate + 2.0*std.error,
         recovered = ifelse(lwr > 0 & lwr < effect_size & upr > effect_size, 1, 0))

# power for the main effect of the familiar music condition
familiarity_main_effect_sims = comb %>% 
  dplyr::filter(term == 'condunfamiliar') %>%
  mutate(sample_size = ifelse(grepl('100', effect_size), 100, 75),
        effect_size = case_when(
            grepl('effect_1_', effect_size) ~ 1,
            grepl('effect_1.5_', effect_size) ~ 1.5,
            grepl('effect_2_', effect_size) ~ 2,
            grepl('effect_2.5_', effect_size) ~ 2.5,
            grepl('effect_3_', effect_size) ~ 3,
         ),
         lwr = estimate -2.6*std.error,
         upr = estimate + 2.6*std.error,
         recovered = ifelse(upr < 0 & lwr < -1*effect_size & upr > -1*effect_size, 1, 0))
```

# Fuzzy plot of each model to look at param fits

```{r}
ggplot(interact_sims, aes(x = dataset_num, y = estimate, color = sample_size)) +
  geom_hline(yintercept = 0, lty = 2) + 
  geom_point() +
  geom_errorbar(aes(ymin=lwr, ymax = upr), width = 0) +
  facet_grid(sample_size~effect_size) +
  theme_bw()



ggplot(familiarity_main_effect_sims, aes(x = dataset_num, y = estimate, color = sample_size)) +
  geom_hline(yintercept = 0, lty = 2) + 
  geom_hline(aes(yintercept = -1*effect_size)) +
  geom_point() +
  geom_errorbar(aes(ymin=lwr, ymax = upr), width = 0, alpha = .5) +
  facet_grid(sample_size~effect_size) +
  theme_bw()
```
# Check for parameter recovery

Summarize the proportion of simulations at each 'true' effect size where the parameter was correctly recovered as 'power'
```{r}
recovery_frame_interaction = interact_sims %>%
  group_by(effect_size, sample_size) %>%
  summarise(recovery_rate = (sum(recovered)+1)/(n()+2),
            se = sqrt(recovery_rate*(1-recovery_rate)/n()), 
            lwr = max(c(0, recovery_rate-2*se)),
            upr = min(c(1, recovery_rate+2*se)),)

recovery_frame_familiarity = familiarity_main_effect_sims %>%
  group_by(effect_size, sample_size) %>%
  summarise(recovery_rate = (sum(recovered)+1)/(n()+2),
            se = sqrt(recovery_rate*(1-recovery_rate)/n()), 
            lwr = max(c(0, recovery_rate-2*se)),
            upr = min(c(1, recovery_rate+2*se)),)


ggplot(recovery_frame_familiarity, aes(x = effect_size, y = recovery_rate, color= factor(sample_size))) +
  geom_point(position = position_dodge(.05)) + 
  geom_line(position = position_dodge(.05)) +
  labs(x = "'True' Effect Size\nInteraction term for the effect of familiar music on internal > external details", y = 'Approximate power') 

interaction_power_figure = recovery_frame_interaction %>% dplyr::filter(sample_size == 75) %>%
  ggplot(data = ., aes(x = effect_size, y = recovery_rate)) +
  geom_point(position = position_dodge(.05)) + 
  geom_line(position = position_dodge(.05)) +
  labs(x = "'True' Effect Size\nInteraction term for the effect of familiar music on internal > external details", y = "Approximate power\nProportion of simulations recovering the 'true' effect") +
  theme_bw()

```
