---
title: "Run Bayesian `brms` models for manipulation checks"
author: "Paul Bloom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r, warning=FALSE, message=FALSE}
library(Matrix)
library(tidyverse)
library(brms)

# Set seed for reproducible run
seed = 11291993
```

For all models, `seed` and `iter` are set so that re-running will yield the same results.


# Load Data

```{r, load_data, message=FALSE, warning=FALSE}
# data with session info
session_data= read_csv('../../data/session_data.csv') 

# scored autobio recall data
recall_data = read_csv('../../data/autobio_interview_scores.csv')
```

# 1. Familiarity Manipulation Check

* Only for clips in the Familiar (`F`) and Unfamiliar (`U`) music conditions
* Cumulative ordinal multilevel model with a probit link function (see Bürkner & Vuorre, 2019)
* Package default weakly-informative priors

```{r, m1, results='hide', warning=FALSE}
m1_familiarity = session_data  %>%
  dplyr::filter(condition %in% c('F', 'U')) %>%
  brms::brm(data = ., familiarity ~ condition + (condition | participant_id), family = cumulative('probit'), cores = 4, 
            iter = 2000, seed = seed)
```

# 2. Music exposure timing manipulation check

* First, make a new `matching` variable that indicates whether reported music exposure in the time period of music release is highest (or tied for highest)
* Then model with multilevel logistic regression
* Package default weakly-informative priors

```{r, m2, results='hide', warning=FALSE}
session_data_time_match = session_data %>%
  dplyr::filter(condition %in% c('F')) %>%
  mutate(.,
         matching = case_when(
                    time == 'child' &
                      childhood_exposure >= adolescence_exposure &
                      childhood_exposure >= young_adult_exposure &
                      childhood_exposure >= adult_present_exposure  ~ 1,
                    time == 'child' &
                      (childhood_exposure < adolescence_exposure |
                      childhood_exposure < young_adult_exposure |
                      childhood_exposure < adult_present_exposure)  ~ 0,
                    time == 'adol' &
                      adolescence_exposure >= childhood_exposure &
                      adolescence_exposure >= young_adult_exposure &
                      adolescence_exposure >= adult_present_exposure  ~ 1,
                    time == 'adol' &
                      (adolescence_exposure < childhood_exposure |
                      adolescence_exposure < young_adult_exposure |
                      adolescence_exposure < adult_present_exposure)  ~ 0,
                    time == 'adult' &
                      young_adult_exposure >= childhood_exposure &
                      young_adult_exposure >= adolescence_exposure &
                      young_adult_exposure >= adult_present_exposure  ~ 1,
                    time == 'adult' &
                      (young_adult_exposure < childhood_exposure |
                      young_adult_exposure < adolescence_exposure |
                      young_adult_exposure < adult_present_exposure)  ~ 0
                  ))


m2_matching = brms::brm(data = session_data_time_match,
                        matching ~ time + (time | participant_id),
                        family = bernoulli(link = 'logit'), cores = 4, 
                        iter = 2000, seed = seed)
```

# 3. Spontaneous Recall

* First remove trials with missing data (0 indicates a skipped trial)
* Then model with multilevel logistic regression
* Package default weakly-informative priors

```{r, m3}
m3_spontaneous = session_data %>%
  dplyr::filter(!is.na(spont_memory), spont_memory !=0) %>%
  mutate(spont_memory = dplyr::recode(spont_memory, 'y'=1, 'n'=0)) %>%
  brms::brm(data = ., spont_memory ~ condition + (condition | participant_id), 
            family = bernoulli(link = 'logit'), cores = 4, 
            iter = 2000, seed = seed)
```


# 4. Coincidence betwen spontaneous and prompted memories

* First remove trials with missing data (0 indicates a skipped trial)
* Make new `coincidence_binary` variable based on whether the `mem_coincidence` variable is a 4 (out of 5) or higher. `coincidence_binary` is also set to 0 if there was not a spontaneous memory on a given trial (i.e. no coincidence)
* Then model with multilevel logistic regression
* Package default weakly-informative priors

```{r, m4s}
session_data_spont_all = session_data %>%
  dplyr::filter(!is.na(spont_memory), spont_memory !=0) %>%
  mutate(spont_memory = dplyr::recode(spont_memory, 'y'=1, 'n'=0)) %>%
  dplyr::mutate(coincidence_binary = ifelse(mem_coincidence >= 4, 1, 0),
                coincidence_binary = ifelse(spont_memory == 0, 0, coincidence_binary))


m4_coincidence = brms::brm(data = session_data_spont_all, 
                           coincidence_binary ~ condition + (condition | participant_id), 
                           family = bernoulli(link = 'logit'), cores = 4, 
                           iter = 2000, seed = seed)
```

# Save all models to the `/results` folder in `.rda` format

```{r, save_data}
save(m1_familiarity,  m2_matching, m3_spontaneous, m4_coincidence, 
     session_data, session_data_spont_all,session_data_time_match,
     file = '../../results/models/manipulation_check_models.rda')
```
