---
title: "Manipulation Check Statistics"
author: "Paul Bloom"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages 
```{r, warning=FALSE, message=FALSE}
library(tidyverse)
library(brms)
library(emmeans)
library(tidybayes)
library(bayestestR)
library(DT)
theme_set(theme_bw())
```

## Load models previously fit in `0a_manipulation_check_models.Rmd`
```{r}
load('../../results/models/manipulation_check_models.rda')
```

# Music Familiarity Manipulation Check (Fig. 4A)

Differences in participant-reported familiarity between clips in the familiar music (`F`) vs. unfamiliar music (`U`) conditions. The table below shows posterior medians and 95% HDI, on the probit scale. 

```{r, warning=FALSE}
# first generate estimated marginal means for each condition with emmeans()
emmeans::emmeans(m1_familiarity, specs = 'condition') %>%
  # pairs() computes all pairwise comparisons
  pairs() %>%
  as.data.frame() %>%
  DT::datatable()
```

# Music Exposure Timing Manipulation Check (Fig. 4B)

Estimates (posterior medians) and 95% HDI for the average proportion of trials where participants rated having the most (or tied for most) exposure during the time period of release, as a function of the time period of release. 

```{r}
matching_table = conditional_effects(m2_matching)[[1]]
dplyr::select(matching_table, -matching, -participant_id, -cond__, -effect1__) %>%
  DT::datatable()
```

# Spontaneous Music-Evoked Recall (Fig. 4C)

All pairwise comparisons for differences in the likelihood of spontaneous memory as a function of condition (`F`=Familiar Music, `U`=Unfamiliar Music, `C`=Non-music clips`). The table below shows posterior medians and 95% HDI for each contrast in log odds.

```{r}
emmeans::emmeans(m3_spontaneous, specs = 'condition') %>%
  pairs() %>%
  as.data.frame() %>%
  DT::datatable()
```


# Coincidence between spontaneous and prompted recall (Fig. 4D)

All pairwise comparisons for differences in the likelihood of coincidence between spontaneous and prompted memory as a function of condition. The table below shows posterior medians and 95% HDI for each contrast in log odds. 

```{r}
emmeans::emmeans(m4_coincidence, specs = 'condition') %>%
  pairs()%>%
  as.data.frame() %>%
  DT::datatable()
```
