---
title: "Make Counterbalances"
author: "Paul A. Bloom"
date: "June 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(stringr)
library(tidyr)
```

## Create counterbalance dataframe

  * 6 different orders for block (C = child, T = teen (adol), A = adult)
  * 6 different orders for condition (F = familiar, U = unfamiliar, C = control (silence))
  * 36 total counterbalance orders -- counterbalanced across subjects
  * Instead of keeping the counterbalances in order, shuffle within each group of 36 to make sure there won't be any 'order effects'
  
```{r}
set.seed(1)
nSubs = 300
seq36 = rep(1:36, nSubs)
bal = tibble(subIndex = 1:nSubs) %>%
  dplyr::mutate(., seq36 = seq36[1:nSubs],
         blockOrder = case_when(
           seq36 <= 6 ~ 'CTA',
           seq36 > 6 & seq36 <= 12 ~ 'CAT',
           seq36 > 12 & seq36 <= 18 ~ 'TCA',
           seq36 > 18 & seq36 <= 24 ~ 'TAC',
           seq36 > 24 & seq36 <= 30 ~ 'ACT',
           seq36 > 30 & seq36 <= 36 ~ 'ATC'),
         conditionOrder = case_when(
           seq36 %% 6 == 0 ~ 'FUC',
           seq36 %% 6 == 1 ~ 'UFC',
           seq36 %% 6 == 2 ~ 'UCF',
           seq36 %% 6 == 3 ~ 'FCU',
           seq36 %% 6 == 4 ~ 'CFU',
           seq36 %% 6 == 5 ~ 'CUF'),
         cb = paste0(blockOrder, conditionOrder),
         set = ceiling(subIndex/36)) %>%
  group_by(set) %>%
  mutate(., 
         cbShuffle = sample(cb)) %>%
  ungroup() %>%
  select(., -cb)


check = bal[37:72,]
length(unique(check$cbShuffle))
```

# Write out counterbalance dataframe

```{r}
bal$subId = paste0('AMFM', stringr::str_pad(bal$subIndex, 3, pad = '0'))
bal = dplyr::select(bal, cb = cbShuffle, subid = subId)


# write it out with date in filename to avoid overwriting if script is rerun
date = gsub(' ', '_', as.character(Sys.Date()))
write.csv(bal, file = paste0('counterbalance_', date, '.csv'), row.names = FALSE)
```
